gratia: An R package for exploring generalized additive models

### 2024-11-21 paper.Rmd
tweak a code block

A distributional GAM for $\mathcal{D}$ Tweedie with linear predictors for $\mu$, $p$, and $\varphi$ is fitted below using *mgcv*'s `twlss()` family
```{r fit-chl-lss-model, cache = TRUE}
m2 <- gam(
  list(
    chl ~ s(lat, lon, bs = "sos", m = -1, k = 150) + # location
      s(jul.day, bs = "cr", k = 20) +
      s(bath, k = 10),
    ~ s(lat, lon, bs = "sos", m = -1, k = 100) +     # power
      s(jul.day, bs = "cr", k = 20) +
      s(bath, k = 10),
    ~ s(lat, lon, bs = "sos", m = -1, k = 100) +     # scale
      s(jul.day, bs = "cr", k = 20) +
      s(bath, k = 10)),
  data = chl, method = "REML", control = ctrl, family = twlss()
)
```

>>>>

A distributional GAM for $\mathcal{D}$ Tweedie with linear predictors for $\mu$, $p$, and $\varphi$ is fitted below using *mgcv*'s `twlss()` family
```{r fit-chl-lss-model, cache = TRUE}
m2 <- gam(
  list(
    chl ~ s(lat, lon, bs = "sos", m = -1, k = 150) + # location
      s(jul.day, bs = "cr", k = 20) + s(bath, k = 10),
    ~ s(lat, lon, bs = "sos", m = -1, k = 100) +     # power
      s(jul.day, bs = "cr", k = 20) + s(bath, k = 10),
    ~ s(lat, lon, bs = "sos", m = -1, k = 100) +     # scale
      s(jul.day, bs = "cr", k = 20) + s(bath, k = 10)
  ),
  data = chl, method = "REML", control = ctrl, family = twlss()
)
```
